plyr: Split-Apply-Combine for Mortals

### 2013-10-20 _posts/2013-04-28-cross-referencing-reviewer-replies-in-latex.md

---
layout: post
title: Cross-Referencing Line Numbers in LaTeX
subtitle: How to make writing reviewer response documents easier.
published: true
---

@@

    We have revised the text. Please see \lr{A1}.

Now, when you compile your document, this will get converted to:

    We have revised the text. Please see page 3, line 23.

And as you modify your manuscript, the page and line numbers will update.

### 2013-10-20 _knitr-posts/2013-10-20-plyr.Rmd
Switch to doParallel

In conjunction with `doMC` (or `doSMP` on Windows) you can run your
function separately on each core of your computer. On a dual core
machine this could double your speed in some situations. Set
`.parallel = TRUE`.

@@

```{r}
library(doMC)
registerDoMC(2)
system.time(llply(x, wait, .parallel = TRUE))
```

>>>>

In conjunction with a package such as `doParallel` you can run your function
separately on each core of your computer. On a dual core machine this make
your code up to twice as fast. Simply register the cores and then set
`.parallel = TRUE`. Look at the `elapsed` time in these examples:

@@

```{r}
library(doParallel)
registerDoParallel(cores = 2)
system.time(llply(x, wait, .parallel = TRUE))
```
